Individual and Differential Harm in Redistricting

### 2022-05-05 paper/paper.Rmd
sf work

Section \ref{sec:motivation} motivates our framework for measuring harm and illustrates the key concepts in the context of partisan gerrymandering for three simple examples.
Section \ref{sec:indiv-harm} formalizes the intuition of Section \ref{sec:motivation} and defines a general measure of individual and differential harm.
Section \ref{sec:estimating} discusses estimating these measures from observed election results.
Section \ref{sec:connections} connects our proposed measures to existing symmetry and fairness measures.
Sections \ref{sec:nj} and \ref{sec:boston} apply the proposed measures to partisan gerrymandering of New Jersey congressional districts and racial impacts of district boundaries on Boston City Council primary elections.
Section \ref{sec:discussion} concludes.

@@

<!-- Despite being derived from individual harm, differential partisan harm is in fact closely related to the overall number of seats won by each party, as Proposition \ref{prop:fairness} describes below. -->
<!-- Yet unlike a simple measure of seats, differential harm is shifted to an interpretable scale, where a value of zero corresponds to fairness. -->
<!-- In other words, differential harm provides a connection between fairness and seats, establishing a normative guide to overall election outcomes. -->
<!-- This connection further supports the use of total seats won by each party as a summary statistic in partisan redistricting simulation methods, as advocated by @deford2020symmetry. -->

>>>>

Section \ref{sec:motivation} motivates our framework for measuring harm and illustrates the key concepts in the context of partisan gerrymandering for three simple examples.
Section \ref{sec:indiv-harm} formalizes the intuition of Section \ref{sec:motivation} and defines a general measure of individual and differential harm.
Section \ref{sec:estimating} discusses estimating these measures from observed election results.
Section \ref{sec:connections} connects our proposed measures to existing symmetry and fairness measures.
Sections \ref{sec:nj}, \ref{sec:alabama}, and \ref{sec:boston} apply the proposed measures to partisan gerrymandering of New Jersey congressional districts, voting rights litigation for Alabama congressional districts, and racial impacts of district boundaries on Boston City Council primary elections.
Section \ref{sec:discussion} concludes.

@@

<!-- Despite being derived from individual harm, differential partisan harm is in fact closely related to the overall number of seats won by each party, as Proposition \ref{prop:fairness} describes below. -->

<!-- Yet unlike a simple measure of seats, differential harm is shifted to an interpretable scale, where a value of zero corresponds to fairness. -->

<!-- In other words, differential harm provides a connection between fairness and seats, establishing a normative guide to overall election outcomes. -->

<!-- This connection further supports the use of total seats won by each party as a summary statistic in partisan redistricting simulation methods, as advocated by @deford2020symmetry. -->
